>

### 2019-04-22 paper/spinifex-paper.tex
step 1

\hypertarget{set-up}{%
\subsection{Set up}\label{set-up}}

@@

In Figure \ref{fig:step0} the contributions of the variables tars1 and
aede2 are mostly orthogonal to the contributions of the other four
variables. These two variables explain the variation of the data
distinguishing the purple cluster from the rest of the sample. Select
aede2 as the manip var, the variable to be manipulated, as it has a
larger contribution to the projection. The question that will be
explored is how important the variable aede2 is to the separation of the
clusters.

>>>>

\hypertarget{step-0-set-up}{%
\subsection{Step 0) Set up}\label{step-0-set-up}}

@@

In Figure \ref{fig:step0} the contribution of the variables
\texttt{tars1} and \texttt{aede2} mostly contrast the contribution of
the other four variables. These two variables combined contribute in the
direction of the projection where the purple cluster is separated from
the other two clusters. The variable \texttt{aede2} is selected as the
manip var, the variable to be controlled in the tour. The question that
will be explored is how important this variable is to the separation of
the clusters.

### 2019-04-22 paper/spinifex_paper.Rmd
step 1

## Set up

@@

<!-- select a manip var-->
In Figure \ref{fig:step0} the contributions of the variables tars1 and aede2 are mostly orthogonal to the contributions of the other four variables. These two variables explain the variation of the data distinguishing the purple cluster from the rest of the sample. Select aede2 as the manip var, the variable to be manipulated, as it has a larger contribution to the projection. The question that will be explored is how important the variable aede2 is to the separation of the clusters.

>>>>

## Step 0) Set up

@@

<!-- select a manip var-->
In Figure \ref{fig:step0} the contribution of the variables `tars1` and `aede2` mostly contrast the contribution of the other four variables. These two variables combined contribute in the direction of the projection where the purple cluster is separated from the other two clusters. The variable `aede2` is selected as the manip var, the variable to be controlled in the tour. The question that will be explored is how important this variable is to the separation of the clusters.
